Applying the optimized ensemble histogram method to the square-well liquid

### 2014-11-04 papers/square-well-liquid/histogram-paper.tex
added round trip rate figure Tested on MAPHost. Took 0:39.62.

@@

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N20-rt}
  \caption{Round trip counts from different methods.}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/periodic-ww130-ff30-N20-rt-rate}
  \caption{Round trip rates from different methods.}
\end{figure}

@@

\textcolor{blue}{Michael (14 November 2014): I tried running this
  method with the end condition that our gaussian has a width 0.5
  times that of our energy range (maximum entropy to low energy
  point), and this is precisely what happened: the simulation got
  stuck pushing down sharp and pointy bubbles. The largest gaussian
  width ever observed was 0.27 times the energy range ($\lambda=1.3$,
  $\eta=0.3$, $N=20$). Furthermore, the gaussian width jumped around a
  good deal during initialization, and I might have to make some
  figures to see what exactly happens to it during initialization.}
